\bigskip GRASS GIS Vector State of the Art -- Gearing towards GRASS GIS 7 \bigskip

### 2014-04-16 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: added 3D house to 3D section
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59752 15284696-431f-4ddb-bdfa-cd5b030d7da7
2014_EGU_G7_Landscape: boxes for TGRASS and PyGRASS, PyGRASS Point and Line code, references with names
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59753 15284696-431f-4ddb-bdfa-cd5b030d7da7

\title{\bigskip GRASS GIS Vector State of the Art  -  Gearing towards GRASS GIS 7 \bigskip}
\author{Markus Metz$^1$, Martin Landa$^2$, Anna Petrášova$^3$, Vaclav Petráš$^3$, Yann Chemin$^4$, Markus Neteler$^1$ and The GRASS GIS Development Team\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka}

@@

@@

\begin{center}
 \includegraphics[width=0.4\textwidth]{images/grass7-3d}
 \newline
 Figure 7: 3D handling
\end{center}
}

@@

% \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{ % special smaller box
\blocknode{References}{
% \scriptsize <<- too small for a poster!
\begin{center}
\begin{tabular}{rp{0.9\textwidth}}
[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[2] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
[3] & Zambelli \& Gebbert \& Ciolli, 2013. PyGRASS: An Object Oriented Python API for GRASS GIS. ISPRS International Journal of Geo-Information 2.1:201-219.\\{}
[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
[5] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU, Czech Republic.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}

>>>>

\title{\bigskip GRASS GIS Vector State of the Art  --  Gearing towards GRASS GIS 7 \bigskip}
\author{Markus Metz$^1$, Martin Landa$^2$, Anna Petrášova$^3$, Vaclav Petráš$^3$, Yann Chemin$^4$, Markus Neteler$^1$ and The GRASS GIS Development Team\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{PyGRASS: fast Python API}{
[Zambelli 2013]

>>> from grass.pygrass.vector.geometry import Point, Line

>>> point = Point()
>>> point.x = 150.65
>>> point.y = 368.50
>>> point
>>> Point(150.650000, 368.500000)
>>> point.distance(Point(160.2, 372.6))
10.39290623454286
%%%%>>> point.get_wkt()
'POINT(150.650000 368.500000)'

>>> line = Line([(5, 12), (6, 13), (4, 19)])
>>> line.bbox()
Bbox(19.0, 12.0, 6.0, 4.0)

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{TGRASS: temporal framework}{
[Gebbert 2014]
}

@@

\begin{center}
\begin{tabular}{lcr}
\includegraphics[width=0.28\textwidth]{images/grass7-3d}
& ~ &
\includegraphics[width=0.49\textwidth]{images/house3D}\\
 Figure X: 3D handling & & Figure X: Chancellor's House, North Carolina State University
\end{tabular}
\end{center}
}

@@

% \blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{ % special smaller box
\blocknode{References}{
% \scriptsize <<- too small for a poster!
\begin{center}
\begin{tabular}{rp{0.8\textwidth}}
[Neteler 2012] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[Gebbert 2014] & Gebbert \& Pebesma, 2014. TGRASS: A temporal GIS for field based environmental modeling, Environmental Modelling \& Software 53:1–12.\\{}
[Zambelli 2013] & Zambelli \& Gebbert \& Ciolli, 2013. PyGRASS: An Object Oriented Python API for GRASS GIS. ISPRS International Journal of Geo-Information 2.1:201-219.\\{}
[Neteler 2005] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. International Journal of Geoinformatics, 1(1):51-61.\\{}
[Landa 2013] & Landa, 2013. Vektorová architektura systému GRASS GIS [GRASS GIS Vector Architecture]. PhD thesis, CTU, Czech Republic.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}
